
The DeviceLink protocol describes the mapping between events and
data on the event and data buses to series of symbols on the
devicelink. It also incorporates the transmission of the relevant
EVENT/data symbols.

The protocols involved are closely linked with the soma RX and TX
protocols. In particular, event and data broadcast are handled
here. The devicelink interface supports four client devices.

All DeviceLink TX activity is organized in a series of 1000-symbol
frames, each frame corresponding to a Soma Event Cycle. The beginning
of each frame is coincident with the beginning of an event cycle, and
is indicated by K28.5.

Event Cycles consist of broadcast messages to up to 80 different
target devices. 


\subsection{TX Link} 

we have an EVENTCE signal, internally, which gates an input event. 

The header consists of:
1. a k28.5 sync comma
2. four 11-symbol device configuration packets:
byte 0: two bits:
bit 0: this device is active during this cycle (DGRANT)
bit 1: This is the start of this device's transmit burst cycle

byte 1: lsb: the first event in the sequence is for this device
byte 2: lsb: the 8th evenet in the sequence is for this device
... through byte 10

The total header duration is 11*4 + 1 = 45 bytes. The events are
subsequently sent on the 49th byte (inclusive to the k28.5), that
is, there are 4 full-events-worth of packets before we start. 


\subsection{RX Link}

Because the RX link operates at *half* the data rate of the TX link,
there are only 500 possible bytes per event cycle.

Devices may send data when their dgrant is asserted, in up to four
bursts of 248 bytes which will be concatenated together. 

To start a burst, send K28.6, to end a burst, send K28.7

To ``commit'' a series of bursts, send K28.4. This aggregates the
previous bursts and places the resulting data packet on the network.


Note that each burst can be a total of 248 bytes long, and
there can be a total of 4 bursts, for 992-byte-length packets. 


If the device has any events, it can send them any time during
the event cycle, but it must first send the data packet.

Any time during an event cycle a device can send an event, which in
this case is a 22-byte packet of data prefaced with a lead comma
character:
  First, the 10-byte bitmask for device target selection
  Then, the 12 bytes of the data itself

The first source of data sends: 
K28.0: first event
K28.1: second sent event
K28.2: third event
K28.3: fourth event

Each MuxEventRX module has a ``clear'' line which, when asserted, will
flush all current IO. Thus if a lock is dropped we can quickly clear
out everything.
